# Introduction to R

- author: Uku-Kaspar Uustalu & Kyle Monahan
- date: 2024-02-16


## Getting Started

R is a statistical platform similar to Stata, SAS, and SPSS. This software allows you to manipulate data, perform descriptive statistics, recoding variables, and bringing in your own data. If you're reading this, you've opened RStudio (the development environment for R) and you're on the way! We will walk through this document together in the workshop.

If you see code that looks like this: `code`, this refers to code that you could write in the R console.

## Set working directory
The first thing we need to do is to set a working directory. Go to Session > Set Working Directory > To Source File location. This is always good practice!

## Comments

You write a comment by adding a # to the start of a line in an R script or the code section in R markdown. Or you could select the lines you wish to comment and press Ctrl/Cmd+Shift+C. We will not be writing a script, only running one, but the idea is the same. The text in GREEN (if you are using the default theme) is a comment.

## Assigning Variables
The first thing we can do is assign a variable. This looks like an arrow placing a value into a variable. Like this: 'n <- 200'.

To assign the variable, we need to run the code below. Click the "Run" button below to assign a variable `n` equal to the value two-hundred. The run button looks like a small play button.

The box below is called an **R code chunk**, and it lets us run R code inside this R markdown notebook.

```{r}
n <- 200
# The variable n is set equal to 200.

# You can write a comment in an RScript by writing a "#"
```

This created a variable `n` which we can access in R. The value appears in the Environment tab, on the upper right-hand side of the window.

> Tip: If you can't see the console window, just click on the word "Console" below. The `>` tells you that R is waiting for your input! The engine is running, and we can either control it with the Run button or the Console directly.

Now if you call n, you will see the console report its value.

```{r}
n
```
## Console Window
YOUR TURN: Try setting 'n <- 300' in the Console Window! After you are done, print 'n'.

If you cannot see the Console Window, click on the word "Console" below.

Try typing 'N' in the Console Window. What happens? The variable 'N' is not found, because 'n' is the name of the variable, not 'N'. R is case-sensitive!
## Functions and Vectors
What if you have multiple numbers to set as a variable? For example, what if we wanted to store the scores we got on exams? These include 94, 96, 72, and 92. (The third test was really hard.)

We use the combine function, which is 'c(n, n, n, ... n)'
```{r}
scores <- c(94, 96, 72, 92)
```
This assigns our scores to the variable "scores" in the Environment. If we call the variable...
```{r}
scores
```
We see the values are printed. This is called a vector. One can access the values within a vector by using square braces '[]'. To get the second score, we use...
```{r}
scores[2]
```
Note that R is one-indexed. To get the first score, we use '[1]', not '[0]'.

## Operators
To check if a vector contains an element, we can use the %in% operator.
```{r}
96 %in% scores
```
It returns TRUE if the vector contains the element...
```{r}
100 %in% scores
```
and FALSE if it does not. TRUE and FALSE are boolean datatypes, also known as logical datatypes in R. These are commonly used to denote binary variables.



## Descriptive Statistics

The best thing about having multiple values to work with is that we can calculate various statistics. Most statistical functions in R easily take a whole vector as input. Let us see what our final semester score would be!
```{r}
mean(scores) # mean
median(scores) # median
sd(scores) # standard deviation
```


## Running from History
Take a look at the History tab on the right next to the Environment tab.
This is where you will find commands you have run in the past.If you double click one, it will auto fill in the Console below.

Select a command from the History tab and double-click on it.
Then select the console window and press Enter/Return to run the command.



## The Environment
Now click on the Environment tab. We see two objects, labeled as Values. These include scores and n.

If you ever forget objects and do not want to click on the Environment tab, you can always call the function objects() for a list of all object names.
```{r}
objects()
```


## Modifying a Vector

Suddenly, we were able to retake a test. Great!
Now we have to replace the value of 72 (the lowest score) with our new score of 85. We can assign the new value to the specific index we want to replace.
```{r}
scores[3] <- 85
```


## Saving Variables and Creating Tables

Re-calculate stats given our retake and create new values to store them.
In R you can store almost anything as a variable, and you should take advantage of that. Always save anything that you might need going forward.

```{r}
scores_mean <- mean(scores)
scores_median <- median(scores)
scores_sd <- sd(scores)
# To store the values, remember to assign them to variables.
```

Now we can create a table with a function called rbind():
```{r}
scores_table <- rbind(
  Mean = scores_mean,
  Median = scores_median,
  SD = scores_sd
)
scores_table
```
When creating the table, we save it as an object (scores_table).
This allows us to refer back to this table at any point later in the script.
```{r}
class(scores_table)
```
We can see that our scores_table is a matrix. Matrices are the most primitive form of table supported in R. Although matrices support both row and column names, they are not best structure to use for working with tabular data.

```{r}
rownames(scores_table)
colnames(scores_table)
```
Note how our column is unnamed. We can easily fix this as follows.
```{r}
colnames(scores_table) <- c("Value")
scores_table
```
You can round values to the nearest whole number using the round() function:
```{r}
round(scores_table)
```
But what if we wanted to keep a certain number of decimal places?
We can use help() to pull up the function's documentation and investigate.
```{r}
help(round)
```
Looks like we can specify an additional argument named "digits" to do this:
```{r}
round(scores_table, digits = 2)
```
Omitting the name of the argument is allowed and does not change the result.
```{r}
scores_table <- round(scores_table, 2)
scores_table
```
Do you think omitting the names of optional arguments is good practice? Why?
Also note how on code above, we first rounded every score in scores_table to two decimal places, creating a new table. Then we assigned this table to the variable scores_table, replacing the previous table.

## Working with Real Data

Now you have mastered the basics of R. But we really want to learn how to import data! So let us do that.

We have a CSV file of the Atlantic Hurricane Database (HURDAT2) 1851-2022. The data is released by the National Hurricane Center (NHC) at NOAA.
```{r}
download.file(url = "https://tufts.box.com/shared/static/gdqc9tdv7334622tkco37oyg9t2fyeaf.csv", destfile = "atlantic.csv")
```

But how do we import this data so we can use it in R?


## Working Directory

All relative file paths in R are relative to the current working directory, which might or might not be the location of the R script, depending on how RStudio was originally launched. If RStudio was launched by double-clicking on the R script or by right-clicking on the R script and then selecting Open With > RStudio, the default working directory will be the location of the R script. Otherwise the default working directory will either be your Documents directory (Windows) or your home directory (macOS and Linux).

We can use getwd() and dir() to explore the current working directory.
```{r}
getwd() # The current location of the working directory.
dir() # The files in the working directory.
```

Your working directory should be the "intro-r-workshop" directory and it should contain both the current script (intro-r.R) and the data file (atlantic.csv). You can use the %in% operator to ensure this is the case.
```{r}
"atlantic.csv" %in% dir()
```
If the statement above returns TRUE, you are all set. But if it returns FALSE, you need to change your working directory. The intro-r.R script and the atlantic.csv data file should have been downloaded to the same location. Ensure that they are both right next to each other in the same folder and then set the working directory to the folder containing your script via Session > Set Working Directory > To Source File Location.

We can ensure the working directory is set correctly by either re-running the commands from above or clicking on the Files tab in the lower-right panel and then selecting More > Go To Working Directory and exploring the results.

## Importing Data

The atlantic.csv data file is in comma-separated values (CSV) format. (Note that the specifics of this format are outlined in standard RFC 4180.) This is a very common data format and you can easily import it in R as follows.
```{r}
hurrdata <- read.csv("atlantic.csv")
```
The read.csv() function has numerous additional optional arguments that we can use to specify how exactly a data file should be read in and interpreted.

To investigate those, we can use the help() function or the ? operator.
```{r}
?read.csv
```
Note that CSV files are different from Excel spreadsheets (XLS or XLSX files) and R does not contain the functionality to import the latter by default. An external community-developed package must be used to import Excel files. Installing and loading external packages is discussed later in this script.

## Exploring Data

We see that a new variable "hurrdata" has been added to the environment.
```{r}
head(hurrdata)
```
This shows us a preview of the fist couple rows of the file.
You can also click on the data table under Environment > Data.

We can use summary() to get descriptive statistics.
```{r}
summary(hurrdata)
```

We might wonder - what type of data is hurrdata?
We imported it from csv, but how is it stored?
```{r}
class(hurrdata)
```
We can see that it is a "data.frame", commonly referred to as a data frame.
A data frame is a table where you have observations as rows and variables as columns. Data frames have some great features for working with data and are the go-to for R data storage. You can think of them almost as spreadsheets.

## Working with Data Frames

Let us say we want to access the maximum wind speed of the sixth observation.
We can do this in multiple ways.
Knowing that "Maximum.Wind" is the ninth column:
```{r}
hurrdata[[6, 9]] # [[row, column]]
hurrdata[[9]][6] # [[column]][row]
```
NOTE: When using a data frame, we must use [[]] to access variable values.
[] will just give us a subset of the data frame, not the values themselves.

Alternatively, we could use the column name:
```{r}
hurrdata[["Maximum.Wind"]][6]
hurrdata$Maximum.Wind[6]
```
Note the dollar sign ($). This is a special operator that allows us to access data.frame variables (columns) based on their name.

The "$" operator is the preferred way of accessing data.frame variables based on their name, as it removes the complexity of when to use [[]] vs [] and does not require quotation marks ... given your column names do not contain spaces.

Note how the read.csv() function automatically replaced spaces with periods in the column names to accommodate this. Underscores are also an acceptable alternative to spaces and other functions might use those instead of periods.

## Selecting Data Based on Conditions

Note how the summary() function from before did not provide much information on the columns containing textual (character/string) data. These columns can be analyzed further using the table() function. Can you guess what it does?
```{r echo = T, results = 'hide'}
table(hurrdata$Name)
```
It creates a frequency table of all the unique values in the column!
But what if we wanted to analyze hurricanes only with a specific name?

We can select rows based on a condition by combining logical operators with [] to subset all the rows where the logical operator returns TRUE. For example, all the hurricanes named Nicole can be extracted as follows.
```{r echo = T, results = 'hide'}
hurrdata[hurrdata$Name == "NICOLE", ]
```

Note that we leave the column index blank to select all the columns.

Alternatively, we could extract values from one column based on the values of another column. For example, the maximum wind speed for all the hurricanes named Nicole could be obtained as follows.
```{r}
max(hurrdata$Maximum.Wind[hurrdata$Name == "NICOLE"])
```


## Data Cleaning: Dates & Strings
Let us say we want to analyze maximum wind speed by year.
Note how the date is stored as a number in YYYYMMDD format.
This notation is great for sorting but very inconvenient for analysis.

We can use the "$" operator to easily extract the Data column as follows.
```{r echo = T, results = 'hide'}
hurrdata$Date
```
Passing this column to the as.character() function will convert all the numbers into text (character data). Note the quotes around the new values.
```{r echo = T, results = 'hide'}
as.character(hurrdata$Date)
```
Let us store these new character (string) representations of the dates in a new variable and use the substr() function to extract the year and the month.
```{r}
date_strings <- as.character(hurrdata$Date)
```
Extract the year from the date string (position 1-4).
```{r}
hurrdata$Year <- substr(date_strings, start = 1, stop = 4)
```
Extract the month from the date string (position 5-6).
```{r}
hurrdata$Month <- substr(date_strings, 5, 6)
```
Convert both new variables to numeric to accommodate further analysis.
```{r}
hurrdata$Month <- as.numeric(hurrdata$Month)
hurrdata$Year <- as.numeric(hurrdata$Year)
```
Note that this is a somewhat hack-y way of dealing with dates. It is suitable for simple conversions like this, but it is highly encouraged to use external packages specifically designed to work with dates for more complex tasks.



## Making a Simple Scatter Plot

Let us say we would like to explore how the maximum wind speed of hurricanes has changed over time. A good visual tool to explore the relationship between two numerical variables is a scatter plot. We can use the built-in plot() function to create a quick and dirty scatter plot examining the relationship between time (denoted by the hurricane year) and hurricane maximum wind speed.
```{r}
plot(hurrdata$Year, hurrdata$Maximum.Wind)
```
Wow, this plot looks quite horrible! Let us try to improve on it...



## Data Cleaning: Missing Data

Why are some wind speeds negative? If we looked into the metadata, we would find that we should have removed these! We can check on the negative data:
```{r}
min(hurrdata$Maximum.Wind)
```
We can combine [] with logical operators like before to find all the values less than zero (< 0) and replace them with "NA", which means "No Data" in R.
```{r}
hurrdata$Maximum.Wind[hurrdata$Maximum.Wind < 0] <- NA
```
We could also delete the whole observation, but this is bad practice!
Let's check on the results. It should print "NA".
```{r}
min(hurrdata$Maximum.Wind)
```
To get the minimum wind speed excluding the NA values, we must call the min() function with na.rm = TRUE to instruct the function to ignore the NA values.
```{r}
min(hurrdata$Maximum.Wind, na.rm = TRUE)
```


## Sampling the Data

We can also sample the data.frame to de-clutter the scatter plot. This is a two-step process in base R. First we use the sample() function to randomly select a desired quantity of row indexes/numbers for our data frame.
```{r}
sample(nrow(hurrdata), 1000)
```
And then we use [] to extract those rows from the data frame.
```{r}
hurrdata2 <- hurrdata[sample(nrow(hurrdata), 1000), ]
```


## Customizing the Scatter Plot

We can now plot the sampled data and use various additional arguments to add a title, axis labels, and customize the visualization to our liking.
```{r}
plot(
  x = hurrdata2$Year,
  y = hurrdata2$Maximum.Wind,
  main = "Selected Annual Hurricane Data, 1851-2022",
  xlab = "Year",
  ylab = "Maximum Wind Speed (knots)",
  pch = 21, # type of symbol to use (see ?points for options)
  col = "blue", # symbol line color
  bg = "lightblue"
) # symbol fill color
```
We can also add a regression line by combining the abline() function with the linear model function. Note the special syntax used to define the formula.
```{r}
abline(
  reg = lm(formula = Maximum.Wind ~ Year, data = hurrdata2),
  col = "red", # line color
  lty = "dashed", # line type
  lwd = 3
) # line width
```
## Base R and the Tidyverse

Thus far we have been working with what is called base R, that is R withoutany community-developed packages installed. Base R has a lot of built-in functionality and can easily do most things, but you may have noticed how some of the code has been a little clunky. Community-developed packages often provide alternative functions that produce the same result using less or more streamlined code and add new functions that do things base R simply cannot.

The most popular collection of R packages is called the Tidyverse, which is specifically designed for data science and often preferred by professionals. Tidyverse is a collection of several different packages, the following of which could be used to recreate our previous analysis using less code.

'readr' is a package used for reading and writing tabular data
'lubridate' is a package specifically designed to work with times and dates
'dplyr' is a package that allows for easy modification of data frames
'ggplot2' is a streamlined and user-friendly data visualization package



## Checking Installed Packages
Depending on what system you are running this script on, you might already have tidyverse installed. This can be easily verified using the Packages tab to the right. Click on the Packages tab to view a list of installed packages. There is also a search bar that allows you to search for a specific package. Try searching for tidyverse to check whether you have it installed or not.

Alternatively we could use the installed.packages() function to see which packages are installed on our system. That function outputs a list of all installed packages. Using the %in% operator from before, we can check whether tidyverse appears in the list of installed packages or not.

```{r}
"tidyverse" %in% installed.packages()
```
This will return TRUE if you have tidyverse installed and FALSE if you do not.



## Installing Packages

We can install new packages using the install.packages() function. However, this function does not check if a package is already installed and will overwrite and re-install the specified package if it is already installed.

Hence you should only use install.packages() to install packages you do not already have installed or to update previously installed packages if needed.

The code block below first checks whether the tidyverse is installed or not.
If it is installed, a message stating so is displayed. Otherwise the function
install.packages() is called to install all of the packages in the tidyverse.
Note that the installation process could take several minutes to complete.

```{r}
if ("tidyverse" %in% installed.packages()) {
  message("Tidyverse already installed!")
} else {
  install.packages("tidyverse")
}
```
You only need to install packages on your machine once. The next time you use R on your computer, all of the tidyverse packages will already be installed.

You can also install packages via the Packages tab by clicking "Install".



## Calling a Library

Before we can use a package, we need to add it to our library. This can be done using the library() command. Using the tidyverse meta-package, we can easily add all of the tidyverse packages into our library at once.

```{r}
library(tidyverse)
```
Note how multiple different packages were attached to our library. Also note the reported conflicts. This means that some of the packages currently loaded into R have functions that share the same name. One of those functions masks the other one and gets called by default. To ensure a specific function from a specific package gets called, use the package::function() notation.

If you received an error stating that there is no package called "tidyverse",please follow the instructions in the previous section to install the package.

You can also include a package in your library by checking the box next to the corresponding package in the Packages tab.



## ADVANCED: Package Management Using Librarian

Keeping track of which packages you have installed could be quite tiresome and continuously re-installing packages is a waste of time. Luckily there are some R packages that make package management in R significantly easier.

One of those packages is librarian. The shelf() command from the librarian package ensures that the package you want is loaded into your library and also installed if needed. This allows you to easily run the same script on different machines without having to worry about installing packages.But be warned that librarian does not display conflict warnings! Hence it is recommended to use the package::function() syntax when using librarian.

Let us install librarian if it is not present and then use it to both install and load a package called janitor that is useful for data cleaning.

```{r}
if (!"librarian" %in% installed.packages()) {
  install.packages("librarian")
}
```

```{r}
librarian::shelf(janitor)
```

## Rewriting the Analysis using Tidyverse

Now let us recreate our previous analysis using packages from the Tidyverse!
First we use read_csv() from the readr package to import the CSV data file.
```{r}
hurrdata3 <- readr::read_csv("atlantic.csv")
```
The readr::read_csv() function is much faster than read.csv() from base R but it does not reformat the column names. Luckily we can use the clean_names() function from the janitor package to convert the column names to snake_case.
```{r}
hurrdata3 <- janitor::clean_names(hurrdata3)
```
The date column can be converted to a date format using lubridate functions.
```{r}
lubridate::ymd(hurrdata3$date)
```
Combining this with mutate() from dplyr allows for easy overwriting.
```{r}
hurrdata3 <- dplyr::mutate(hurrdata3, date = lubridate::ymd(date))
```
Now we can combine the mutate() function from dplyr with the lubridate year() and month() functions to easily create new columns for the year and month.
```{r}
hurrdata3 <- dplyr::mutate(hurrdata3,
  year = lubridate::year(date),
  month = lubridate::month(date)
)
```
Dplyr can also easily convert values to NA and sample rows from a table.
```{r}
hurrdata3 <- dplyr::mutate(hurrdata3,
  maximum_wind = dplyr::na_if(maximum_wind, -99)
)

hurrdata4 <- dplyr::sample_n(hurrdata3, 1000)
```


## Alternate (Better) Data Visualizations

Now we can use the popular ggplot2 graphing library to visualize our data.The ggplot2 library is included in the tidyverse and follows a layered logic.

First you specify the data frame of interest using the ggplot() function and then you create a mapping between variables (columns) and axes using the aes() function. This defines the plotting environment and we can add layers to the plot using the + operator. For example, geom_point() will generate a point for each x and y combination as specified with ggplot() and aes().

The plot object can be saved in a variable and then displayed by calling it.
```{r}
hurrgraph <- ggplot(data = hurrdata4, aes(x = year, y = maximum_wind)) +
  geom_point()
```

```{r}
hurrgraph
```
Note how the default plot looks slightly better than what the plot() function produces, but it is still quite bad. Luckily ggplot2 provides us with several customization options and we can tailor the visualization to our needs.
```{r}
hurrgraph2 <- ggplot(
  data = hurrdata4,
  aes(x = year, y = maximum_wind, color = maximum_wind)
) +
  geom_point() + # add the initial points
  scale_color_gradient(low = "blue", high = "red") + # generate color scheme
  theme(legend.position = "bottom") + # put the legend on the bottom
  ylab("Maximum Wind Speed (knots)") + # change the y-label
  ggtitle("Selected Annual Hurricane Data, 1851-2022") + # add a title
  theme(plot.title = element_text(lineheight = 0.8, face = "bold")) + # format
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 0.5))
```

```{r}
hurrgraph2
```
While ggplot2 might appear to be more complicated to use than the built-in plot() function, it is actually much easier to create complex (and beautiful) data visualizations using ggplot2 than built-in graphing functionality. Many professionals also prefer ggplot2 and it is prevalent in various guides.



## ADVANCED: Piping and Grouping

Was it correct of us to sample the data given our hypothesis?
A closer look at it reveals that the data contains several entries for each hurricane at different points of intensity. Hence our approach was wrong.

To see how the maximum wind speed of hurricanes has changed over time, we should be looking at the maximum wind speed of each hurricane at its highest point of intensity. We can use functions from dplyr to extract those.
```{r}
hurrdata5 <- hurrdata3 %>%
  dplyr::group_by(name, year) %>%
  dplyr::summarize(
    maximum_wind = max(maximum_wind),
    .groups = "drop"
  )
```
The pipe operator %>% from the magrittr library is often used to combine several functions into a data analysis pipeline. The pipeline above finds the maximum value of the maximum_wind column for each unique hurricane name and year combination. The pipe operator takes whatever is passed to it and feeds it into the next function as the first argument. Tidyverse functions are built to work with the pipe operator but other functions might not be.

Now we can correctly visualize the change in maximum wind speed over time.
```{r}
hurrgraph3 <- ggplot(data = hurrdata5, aes(x = year, y = maximum_wind)) +
  geom_point() +
  geom_smooth(method = lm, formula = y ~ x) + # add a linear trend line
  ylab("Maximum Wind Speed (knots)") +
  ggtitle("Hurricane Wind Speeds at Highest Intensity 1851-2021")
```

```{r}
hurrgraph3
```


## EXERCISE: Fix the Analysis

Do you think we made a good graph that tells an accurate story?
Take a look at the year 1950. What do you think causes this sudden change?
Are we correctly extracting the maximum wind speed for each unique hurricane?
Is it fair to be comparing all the recorded hurricanes from 1850 until 2022?
Should we instead be looking at the most intensive hurricane from each year?

Fix the analysis above and produce a graph that answers the question:
How has the intensity of hurricanes changed over time?



## OPTIONAL: Interactive Graphics

We can easily create interactive data visualization in R using the plotly package. Plotly is not included in the tidyverse, so we have to install it (unless it is already installed) and load it into our library. We can use the shelf() function from the librarian package to easily do this as before.

```{r}
librarian::shelf(plotly)
```

```{r}
hurrdata6 <- hurrdata3 %>%
  dplyr::group_by(year) %>%
  dplyr::summarize(
    count = dplyr::n_distinct(id),
    .groups = "drop"
  )
```

```{r}
hurrgraph4 <- plotly::plot_ly(
  data = hurrdata6,
  x = ~year,
  y = ~count,
  type = "bar",
  marker = base::list(
    color = "lightblue",
    line = base::list(
      color = "blue",
      width = 0.5
    )
  )
) %>%
  plotly::layout(
    title = "Number of Hurricanes 1851 - 2022",
    xaxis = base::list(title = "Year", tickangle = 45),
    yaxis = base::list(title = "Recorded Number of Hurricanes")
  )
```

```{r}
hurrgraph4
```

## BONUS: Defining Functions

(Un)likely scenario: Suddenly you need to work with parametric equations.

For those of you who do not know, a parametric equation is where the x and y coordinates are both written in terms of another variable. This variable is called a parameter and is usually denoted with the letter t.

Let us say we were given the following parametric equation...
```{r}
x <- 16 * sin(t)^3
y <- 13 * cos(t) - 5 * cos(2 * t) - 2 * cos(3 * t) - cos(4 * t)
```
...and asked to solve it for t ranging from 0 to 2*pi.

We can easily define our parameter as follows.
```{r}
t <- seq(0, 2 * pi, by = 0.1)
```
However, calculating all the x and y values would be extremely tedious if we had to do it manually. Luckily we can use R to make our computer do it for us. All we need to do is just tell R how to calculate these values by defining functions that take t as input and return the value of either x or y.

We can define the one for x as follows.
```{r}
get_x <- function(t) {
  x <- 16 * sin(t)^3
  return(x)
}
```
Alternatively, we could also define it in one one line. We will do this for y. A one-line function like this is sometimes also called a lambda function.
```{r}
get_y <- function(t) 13 * cos(t) - 5 * cos(2 * t) - 2 * cos(3 * t) - cos(4 * t)
```
Now we can easily store all of our t, x, and y values into a data frame
```{r}
parameq <- data.frame(t = t)
parameq$x <- get_x(parameq$t)
parameq$y <- get_y(parameq$t)
```
Finally, let us plot the results of our parametric equation.
What do you think it will look like? Try to guess.

Note that this whole section on parametric equations was added for a very special version of this workshop that ran on February 14. Does that help?

```{r}
finalplot <- ggplot(data = parameq, aes(x = x, y = y)) +
  geom_polygon(
    linetype = "solid",
    linewidth = 1.5,
    color = "black",
    fill = "red"
  )
```

```{r}
finalplot
```


## FAQ

You might wonder what is the difference between "=" and "<-"?
Well, that is a good question and beyond the scope of this tutorial.But it is all about scope.

When you create a variable, it is always within some area that limits from where it is accessible, commonly called a scope.

"<-" puts a value in the user's workspace, which makes it accessible by said user anywhere, whereas "=" declares it in the scope of a function.
